A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-03-17 paper/paper.tex
lics23, paper: minor changes

\subsection{Relating the indexed representation to parametricity\label{sec:indexed-param}}
% \begin{equation*}
%   \Sigma S: \U.\, S\rightarrow T ~\simeq~ T \rightarrow \U
% \end{equation*}

>>>>

\subsection{Relating the indexed representation to parametricity\label{sec:indexed-param}}
The correspondence between fibered and indexed representation is a particular case of the Grothendieck construction, and can be written as:
\begin{equation*}
  (\Sigma S: \U. (S \rightarrow T)) \simeq (T \rightarrow \U)
\end{equation*}
